%!TeX program = pdflatex
% Geoff Boeing's Curriculum Vitae
% Email: boeing@usc.edu
% Web: https://geoffboeing.com/
% Repo: https://github.com/gboeing/cv

\documentclass[11pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{setspace} % custom line spacing

% what is your name?
\newcommand{\myname}{Alisher Juzgenbayev}

% select default typefaces
\usepackage{ebgaramond} % document's serif typeface
\usepackage{tgheros}    % document's sans serif typeface

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % increase sans serif headings tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.9}

% define space between list items
\newcommand{\listitemspace}{0.25em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdfkeywords = {city planning, housing, street networks, transportation, urban design, urban informatics},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright{}

    % display your name as the document title
    \namefont{\myname}

    % affiliation and contact info blocks
    \vspace{1em}
    \begin{minipage}[t]{0.700\textwidth}
        % current primary affiliation, left-aligned
        Department of Political Science \\
        Pritzker School of Law \\
        Northwestern University
    \end{minipage}
    \begin{minipage}[t]{0.295\textwidth}
        % contact info details, right-aligned
        \flushright{}
        \href{mailto:juzgenbayev@u.northwestern.edu}{juzgenbayev@u.northwestern.edu} \\
        +1 773 349 0612 \\
        \href{https://alisher.site}{alisher.site}
    \end{minipage}


    \section*{Education}

    \begin{tablist}

        \item[Ph.D.] \tab{}Political Science, Northwestern University, 2027 (expected)
        \item[J.D.] \tab{}Pritzker School of Law, Northwestern University, 2027 (expected)
        \item[M.A.]  \tab{}Political Science, Northwestern University, 2022
        \item[B.S.]  \tab{}Political Science and International Relations, \textit{summa cum laude}, Nazarbayev University, 2020

    \end{tablist}





    \section*{Research Areas}

    \begin{itemize}

        \item Comparative Politics: Institutions, Non-Democratic Regimes, Comparative Courts, Former Soviet Union.
        \item Law: Empirical Legal Research, Federal Jurisdiction, Civil Procedure, Constitutional Law, Consumer Law.
        \item Methodology: Comparative Historical Analysis, Experiments, Open Science. 

    \end{itemize}



    \section*{Publications}

   \subsection*{Journal Articles}

   \begin{tablist}

       

        \item[2024] \tab{}Alisher Juzgenbayev. \enquote{\href{https://doi.org/10.1017/jlc.2024.17}{Framing the Judiciary: Effects of Partisan, Procedural, and Populist Frames on Apex Court Perceptions in Czechia.}} \textit{Journal of Law and Courts}, available First View.

      

    \end{tablist}



    \subsection*{Book Chapters}

    \begin{tablist}

        \item[2023] \tab{}A. Trochev, A. Juzgenbayev. \enquote{Instrumentalization of Constitutional Law in Central Asia.} In: \textit{Research Handbook on Law and Political Systems} (pp. 139--168), edited by R. M. Howard, K. A. Randazzo, and  R. A. Reid. Cheltenham, England:\ Edward Elgar. \href{https://doi.org/10.4337/9781800378346.00014}{doi: 10.4337/9781800378346.00014}

    \end{tablist}

    \subsection*{Blog Posts}

    \begin{tablist}
        
        \item[2019] \tab{}A. Juzgenbayev.\enquote{Ex-President Arrested in Kyrgyzstan: Constitutional Tribunal in Central Asia in the Center of High Politics.} \href{http://www.iconnectblog.com/2019/08/ex-president-arrested-in-kyrgyzstan-constitutional-tribunal-in-central-asia-in-the-center-of-high-politics/}{Int’l J. Const. L. Blog}. 
        \item[2019] \tab{}A. Juzgenbayev. \enquote{Constitutional Tribunal in Kyrgyzstan Decides Against the Former President, Clearing the Way for His Prosecution.} \href{http://www.iconnectblog.com/2019/11/constitutional-tribunal-in-kyrgyzstan-decides-against-the-former-president-clearing-the-way-for-his-prosecution/}{Int’l J. Const. L. Blog}.
    \end{tablist}


    \section*{Invited Talks}

   \begin{tablist}

    \item[2024] \tab{}\enquote{Framing the Judiciary: Effects of Partisan, Procedural, and Populist Frames on Apex Court Perceptions in Czechia.} Judicial Studies Institute. Masaryk University, Brno, Czech Republic (online). 
    
    \item[2024] \tab{}\enquote{In-group-motivated evaluations of domestic violence and the mitigating role of the highly visible events.} Models, Experiments, and Data Workshop. University of Wisconsin-Madison, Madison, Wisconsin (online). (With Valeriia Umanets, Yulia Khalikova, and Marcy Shieh). Sep. 13.

    \end{tablist}

    


    \section*{Conference Activity}

    

    \subsection*{Conference Papers Presented}

    \begin{tablist}

        \item[2024] \tab{}A. Juzgenbayev. \enquote{Populist Frames and Judicial Legitimacy: Survey Experiment in Czech Republic.} European Consortium For Political Research General Conference.  Prague, Czechia. Sep 4--8. 

        \item[2022] \tab{}A. Juzgenbayev and A. Trochev. \enquote{Clientelism, Constitutional Courts, and High Politics in Central Asian Countries.} Association for Slavic, East European, and Eurasian Studies Convention. Chicago, Illinois. Nov 10--13.

    \end{tablist}



    \section*{Grants and Awards}



    \subsection*{Competitive Grants and Fellowships}

    \begin{tablist}


        \item[2023] \tab{}Northwestern University, Graduate Conference Travel Grant (\$800)
        \item[2023] \tab{}Buffett Institute, International Conference Travel Grant (\$1,000)
        \item[2023] \tab{}Northwestern University, Graduate Research Grant (\$3,000)
        \item[2021] \tab{}Harvard Ukrainian Studies Institute, Summer Institute Scholarship (\$1,600)
        \item[2021] \tab{}Radulovacki Slavic Studies, Ukrainian Study Grant (\$5,200)
        \item[2019] \tab{}Visiting International Students Program at University of Wisconsin-Madison (\$14500)
        \item[2019] \tab{Young Researchers Alliance Undergraduate Research Grant (\$500)} 

    \end{tablist}

    \subsection*{Awards and Honors}

    \begin{tablist}

        \item[2020] \tab{}European Universities Debating Championship, Semi-Finalist. 
    \end{tablist}

    \section*{Teaching}

    \subsection*{Teaching Assistance}

    \begin{tablist}
        

        
        \item[2024--]      \tab{}Civil Procedure; Introduction to Comparative Politics.
        \item[2023--24]    \tab{}Civil Procedure; Property.
        \item[2021--22]    \tab{}Law in Political Arena; International Law and Politics; Global Development.
        \item[2017--18]    \tab{}Quantitative Methods in Political Science; International Relations (Academic Writing).

    \end{tablist}



    \section*{Leadership \& Service}



    \subsection*{Academic Journal Editorship}

    \begin{tablist}

        \item[2023--24]  \tab{}\textit{Northwestern University Law Review}, Senior Empirical Editor, Vol. 119. 


    \end{tablist}

   

    \subsection*{Service to the University}

    \begin{tablist}
        \item[2024--]   \tab{}Northwestern Political Science Department, Comparative Politics Workshop Graduate Coordinator.
        
    \end{tablist}


    \subsection*{Leadership}

    \begin{tablist}
        \item[2023--24] \tab{}Pritzker School of Law, American Constitution Society, Director for External Affairs.
        \item[2023--24] \tab{}Pritzker School of Law, ACLU, VP for Activism.
        \item[2019] \tab{} Nazarbayev University, Association of Political Science Students, President.
        \item[2017--19] \tab{} Nazarbayev University, Student Debate Society, Board Member \& Coordinator.
    \end{tablist}


   



    \section*{Peer Review}


    \begin{itemize}

        \item \textit{Journal of Law and Courts}
      

    \end{itemize}

  



    \section*{Memberships}

    \begin{itemize}

        \item Federal Bar Association
        \item American Immigration Lawyers Association
        \item American Political Science Association

    \end{itemize}






 

    \section*{Professional Employment}

    \begin{tablist}

        \item[2024] \tab{}Legal Aid Chicago, Consumer Practice Group. Summer Intern.
        \item[2023] \tab{}United States District Court for the Northern District of Illinois. Judicial Extern.
 

    \end{tablist}


    \section*{Language and Skills}

    \subsection*{Languages}
        Russian (Native); Ukrainian (Reading Knowledge); Kazakh (Intermediate).
    \subsection*{Computing}
        \LaTeX, R, Qualtrics.
    
    % display today's date as Month Year after a vertical space below the end of the text
    \begin{center}
        \vfill
        Updated \monthyeardate\today
    \end{center}

\end{document}
